\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,bmargin=1in,tmargin=1in]{geometry}
\usepackage{style}

\pagenumbering{gobble}

% -------------------
% Content
% -------------------
\begin{document}

% TItle
\begin{center} 
\bfseries
\color{scred}
\LARGE Syllabus Quick Facts \par\vspace{0.2\baselineskip}
\Large MATH 141: Calculus I --- Fall 2025
\end{center} \pspace


% Course Information
\mysection{0.27}{Course Information}{course_info}
\hspace{0.53cm} {\itshape Instructor Email}: \href{mailto:cm264@mailbox.sc.edu}{cm264@mailbox.sc.edu} \par
\hspace{0.53cm} {\itshape Course Webpage}: \href{https://coffeeintotheorems.com/courses/2025-2/fall/math-141/}{https://coffeeintotheorems.com/courses/2025-2/fall/math-141/} \par
\hspace{0.53cm} {\itshape Office Hours}: The instructor's office is LeConte 345C. The office hours are Monday, Wednesday, \par \hspace{0.55cm} and Friday from 2:00pm to 3:00pm, and Tuesday/Thursday from 1:00pm until 2:00pm. \pspace


% Grading Components
\mysection{0.27}{Grading Components}{grade_comp}
Course grades are determined by the following components: \par \vspace{-0.3cm}
	\begin{table}[!ht]
        \begin{tabular}{lr}
	Check-Ins & 5\% \\
	Labs & 10\% \\
	Gateway Exams & 10\% \\
	Homework & 20\% \\
	Exam I--III & 30\% \\
	Final Exam & 25\%
        \end{tabular} 
        \end{table}


% Attendance 
\mysection{0.27}{Attendance}{attendance}
Attend each lecture and show up on time. Address any absences---anticipated or otherwise---with the instructor. If you miss a lecture, you are responsible for any material covered, any work assigned, any course changes made, etc. during the class. Five or more unexcused absences from lectures could result in receiving a grade penalty per additional absence or an `F' in the course. Furthermore, excessive lateness will also count as an absence. 
\pspace


%% CircleIn 
%\mysection{0.27}{CircleIn}{circlein}
%Students are expected to participate in the course using CircleIn. This participation consists of two components: weekly feedback and CircleIn Study Actions. Students need to submit weekly check-ins and complete a total of at least 10 specific types of CircleIn interactions throughout the semester. 
%\pspace


% Check-Ins 
\mysection{0.27}{Check-Ins}{check}
There will be a check-ins \textit{every} class, typically at the start of class. Because solutions will often then be immediately discussed, no make-up check-ins will be given (except under extraordinary circumstances). \pspace


% Labs 
\mysection{0.27}{Labs}{labs}
Nearly every week, students will have a lab to complete in Python. These labs will help engage them with the material and learn some basic programming skills. Students will have a designated lab time to work on these labs. However, if a student does not complete their lab during this time, they are still expected to complete and submit the lab on time.
\pspace


% Gateways 
\mysection{0.27}{Gateways}{gateways}
There are two Gateway exams during the semester. The Gateway exams are 30~minute exams that will help students to achieve mastery over basic Precalculus (Gateway~I) and differentiation (Gateway~II) skills and help assure students that they are prepared for the future material. 
\pspace



\newpage



% Homeworks 
\mysection{0.27}{Homeworks}{homeworks}
There will be weekly homework assignments. Homeworks will mostly be given and submitted using MyLab. Therefore, students will need to purchase an access code to this system at \url{http://www.mymathlab.com}. Students can also purchase access to a digital copy of the textbook when they purchase an access code.
\pspace


% Exams 
\mysection{0.27}{Exams}{exams}
There will be three exams in this course, each worth 10\% of the course grade for a total of 30\% of the course grade. There will also be a final exam worth 25\% of the course grade. Together, all exams are worth 55\% of the course grade. 
\pspace


% Course Schedule 
\mysection{0.27}{Course Schedule}{schedule}
The following is a \emph{tentative} schedule for the course and is subject to change. 
        \begin{table}[!ht]
        \centering
        \scalebox{0.78}{%
        \begin{tabular}{ll || ll}
        Date & Topic(s) & Date & Topic(s) \\ \hline         
	08/19 & Gateway~I & 10/14 & Lab 7 \\
	08/20 & Graphical Limits & 10/15 & Optimization \\
	08/21 & Lab 1 & 10/16 & Recitation \\
	08/22 & Graphical \& Special Limits & 10/17 & Optimization \\
	08/25 & Special Limits & 10/20 & Review \\
	08/26 & Gateway~I & 10/21 & Recitation \\
	08/27 & Special Limits & 10/22 & Exam Review \\
	08/28 & Recitation & 10/23 & Exam Review \\
	08/29 & Special Limits & 10/24 & Exam 2 \\
	09/01 & Labor Day (No Classes) & 10/27 & IVT \\
	09/02 & Recitation & 10/28 & Lab 8 \\
	09/03 & Continuity & 10/29 & MVT \\
	09/04 & Lab 2 & 10/30 & Recitation \\
	09/05 & Derivative Introduction & 10/31 & Integral Introduction \\
	09/08 & Derivative Rules & 11/03 & Integral Introduction \\
	09/09 & Lab 3 & 11/04 & Recitation \\
	09/10 & Derivative Rules & 11/05 & Fundamental Theorem of Calculus \\
	09/11 & Recitation & 11/06 & Lab 9 \\
	09/12 & Derivative Rules & 11/07 & Fundamental Theorem of Calculus \\
	09/15 & Tangents \& Linearizations & 11/10 & Area \\
	09/16 & Review & 11/11 & Recitation \\
	09/17 & Graphical Derivatives & 11/12 & Area \\
	09/18 & Lab 4 & 11/13 & Recitation \\
	09/19 & Exam 1 & 11/14 & $u$-Substitution \\
	09/22 & Max/Min/Inflections & 11/17 & $u$-Substitution \\
	09/23 & Lab 5 & 11/18 & Recitation \\
	09/24 & l'H\^{o}ptal's Rule & 11/19 & $u$-Substitution \\
	09/25 & Gateway~II & 11/20 & Exam Review \\
	09/26 & l'H\^{o}ptal's Rule & 11/21 & Exam 3 \\
	09/29 & l'H\^{o}ptal's Rule & 11/24 & Thanksgiving Break (No Class) \\
	09/30 & Recitation & 11/25 & Thanksgiving Break (No Class) \\
	10/01 & Implicit Differentiation & 11/26 & Thanksgiving Break (No Class) \\
	10/02 & Lab 6 & 11/27 & Thanksgiving Break (No Class) \\
	10/03 & Implicit Differentiation \& Related Rates & 11/28 & Thanksgiving Break (No Class) \\
	10/06 & Related Rates & 12/01 & Volumes by Disk/Shell \\
	10/07 & Recitation & 12/02 & Lab 10 \\
	10/08 & Related Rates \& Optimization & 12/03 & Volumes by Disk/Shell \\
	10/09 & Fall Break (No Class) & 12/04 & Recitation \\
	10/10 & Fall Break (No Class) & 12/05 & Volumes by Cross Section \\
	10/13 & Optimization & 12/(8,10,12) & Final Exams
        \end{tabular}
        }
        \end{table}

\end{document}