\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=0.9in,rmargin=0.9in,bmargin=0.9in,tmargin=0.9in]{geometry}
\usepackage{style}

\setlength{\parindent}{0ex}

% -------------------
% Content
% -------------------
\begin{document}

\begin{center} {\bfseries \Large MATH 115 (08/28): Sets, Geometry, \& Function Problems} \end{center} \par\vspace{1cm}

% Problem 1
\prob Consider the intervals $A= [-3, 3]$, $B= (-2, 1]$, $C= [0, 5]$, $D= \{ 0 \}$, $E= (-2, -1)$, and $F= (1, 4)$. Expressing your answer as simply as possible, compute the following:
	\begin{2enumerate}
	\item $A \cap B$
	\item $A \cup C$
	\item $B \cap D$
	\item $A \cup F$
	\item $C \cap F$
	\item $A \cap (E \cup F)$
	\end{2enumerate} \pspace



% Problem 2
\prob Define the points $A= (-1, 3)$, $B= (1, 1)$, and $C= (2, 6)$. 
	\begin{2enumerate}
	\item Find the distance from $A$ to the $y$-axis.
	\item Find the distance from $C$ to the $x$-axis.
	\item Find the slope of the segment connecting \par $A$ and $B$.
	\item Find the midpoints of $AC$.
	\item Find the distances between each pair of points.
	\item Is the triangle formed by $ABC$ a right triangle? Explain. 
	\end{2enumerate} \pspace



% Problem 3
\prob Consider the relation given by $x= y^2 + y - 12$.
	\begin{enumerate}[(a)]
	\item Find a point on the graph given by this equation. 
	\item Is $(-18, -2)$ on the graph given by this equation? Explain.
	\item Is the given relation a function of $x$? Explain. 
	\item Is the relation a function of $y$? Explain. 
	\item Find the $x$-intercepts for the graph of this relation. 
	\item Find the $y$-intercepts for the graph of this relation. 
	\end{enumerate} \pspace



% Problem 4
\prob A rope is attached to the tip of a boat. The rope is pulled taunt over a pulley suspended 8~ft above the ground at the edge of the water. The boat is 30~ft from the shore and rope is being pulled over the pulley at a rate of 2~ft per second. Find the distance the tip of the boat is from the shore after $t$~seconds. \pspace



% Problem 5
\prob Simplify the following as much as possible:
	\begin{enumerate}[(a)]
	\item $\dfrac{x^4 (x^5 y^{-2})^{-3}}{x^{-1} (x y)^5 (x^0 y^{-8})}$
	\item $\left( \dfrac{x^{-2}}{y^4} \right)^{-5} \sqrt{\dfrac{x^4}{y^2}}$
	\item $\left( \left( \dfrac{(x^0 y^5)^{-2} y^4 x^{-2}}{x^{-10} y^5} \right)^2 \right)^{-1}$
	\end{enumerate}



\newpage



% Problem 6
\prob Consider the relation given by $f(x)= \dfrac{x + 3}{x}$.
	\begin{2enumerate}
	\item Is $f(x)$ a function? Explain. 
	\item Find a point on the graph given by $f(x)$? \par Explain.
	\item Is $(-1, -2)$ on the graph given by $f(x)$? \par Explain.
	\item Is $\pi$ in the domain of $f(x)$? Explain.
	\item Is $0$ in the domain of $f(x)$? Explain. 
	\item Find something in the range/image of $f(x)$. Justify your answer. 
	\item Is $5 \in \text{im f}$, i.e. $5 \in \text{range}(f)$? Justify your answer. 
	\item Do the graphs of $f(x)$ and $g(x)= 2(3 - x)$ intersect? Explain. 
	\item Find and simplify $f(1 + a)$. 
	\end{2enumerate} \pspace



% Problem 7
\prob Complete the following:
	\begin{enumerate}[(a)]
	\item Find an expression `describing' the set of all points a distance 5 from the point $(4, -3)$. 
	\item Find the equation of a circle with center $(1, 7)$ that intersects the $x$-axis only once. 
	\item Sketch a relation whose domain is the positive real numbers and passes the vertical line everywhere except at $x= 5$.
	\item Let $\mathcal{O}$ be the origin and $P$ be the point in Quadrant~II where the graph of $f(x)= 6 - x^2$ intersects the line $y= 4$. Find the area of the rectangle that has $\mathcal{O}P$ as one of its diagonals. 
	\end{enumerate} \pspace



% Problem 8
\prob Let $A= \{ 0, 1, 2, 3 \}$ and $B= \{ -1, 0, 1, 5, 9 \}$. 
	\begin{enumerate}[(a)]
	\item Give an example of a relation from $A$ to $B$ that is not a function. 
	\item Give an example of a function from $A$ to $B$. 
	\item Give an example of a function from $A$ to $B$ that is not constant but is constant on the subset of $A$ given by $\{ 0, 2 \}$. 
	\item Give an example of a function from $A$ to $B$ that is increasing. 
	\item Give an example of a function from $A$ to $B$ that is not increasing. 
	\item Is it possible to define a function from $A$ to $B$ whose range and codomain are the same? Explain. 
	\end{enumerate} \pspace



% Problem 9
\prob Let $F(x)= \dfrac{\sqrt{x + 3}}{x - 2}$. 
	\begin{enumerate}[(a)]
	\item Is $F(x)$ a function of $x$? Explain. 
	\item What is the domain of $F(x)$?
	\item What is $F(10)$? What is the corresponding point on the graph of $F(x)$?
	\item Find the $x$- and $y$-intercepts for $F(x)$. 
	\item Is $-2 \in \text{range} \left( F(x) \right)$? Explain. 
	\end{enumerate}


\end{document}