\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,bmargin=1in,tmargin=1in]{geometry}
\usepackage{
	enumerate,		% Enumerate Environments
	microtype,			% Improved Typesetting
	multicol,			% Use Multiple Columns
}

% -------------------
% Fonts
% -------------------
\usepackage[T1]{fontenc}
\usepackage{charter}

\setlength{\parindent}{0ex} % Paragraph Indentation

% -------------------
% Commands
% -------------------
\newcommand\ds{\displaystyle}
\newenvironment{3enumerate}{%
	\begin{enumerate}[(1)]
	\begin{multicols}{3}
	}{%
	\end{multicols}
	\end{enumerate}
}

\newcounter{problem}
\newcommand{\prob}{\stepcounter{problem}%
\noindent\textbf{Problem \theproblem. }}

\newcommand{\pspace}{\par\vspace{\baselineskip}}

% -------------------
% Tikz/PGFPlots
% -------------------
\usepackage{pgfplots}
\pgfplotsset{compat=newest}


% -------------------
% Content
% -------------------
\begin{document}
\pagenumbering{gobble}

% Title
\begin{center} {\bfseries \LARGE Linear Function Problems --- 01/28} \end{center} \par\vspace{0.2\baselineskip}

% Problem 1
\prob Does the table below represent a linear function? \par
	\begin{table}[ht]
	\centering
	\begin{tabular}{|c||rrrr|} \hline
	$x$ & $1$ & $2$ & $5$ & $6$ \\
	$y$ & $7$ & $4$ & $-5$ & $-8$ \\ \hline
	\end{tabular}
	\end{table} \par
If $y$ is a linear function of $x$, find the function. If it is not, explain why. \pspace



% Problem 2
\prob A company is examining their operating costs. They observe that the amount they spend making each item they sell is approximately the same---roughly \$8. The company also has to pay \$7,500 in rent for their warehouse used in manufacturing. 
	\begin{enumerate}[(a)]
	\item Explain why the total cost of production, $C$, is a linear function of the number of items they produce, $q$. Find $C(q)$.
	\item Find and interpret the slope of $C(q)$.
	\item Find and interpret the $y$-intercept of $C(q)$.
	\item What is the cost of producing 450 items?
	\end{enumerate} \pspace


% Problem 3
\prob A statistician finds that the population of a town $t$~years after its founding in 1980 is given by $P(t)= 200t + 8500$. 
	\begin{enumerate}[(a)]
	\item What kind of model did the statistician use? Justify your answer.
	\item Find and interpret the average rate of change for $P(t)$.
	\item Find and interpret the $y$-intercept for $P(t)$.
	\item Find and interpret $P(20)$.
	\item According to this model, what is the year that the town will be 100,000 people?
	\end{enumerate} \pspace



% Problem 4
\prob Find the average rate of change for $f(x)= x^2 - 3x + 5$ between $x= -1$ and $x= 5$. Interpret this average rate of change graphically. \pspace



% Problem 5
\prob Find the linear function that passes through the point $(1, 3)$ with slope $-4$. \pspace



% Problem 6
\prob Find the linear function shown below. 
	\[
	\fbox{
	\begin{tikzpicture}[scale=0.8,every node/.style={scale=0.5}]
	\begin{axis}[
	grid=both,
	axis lines=middle,
	ticklabel style={fill=blue!5!white},
	xmin= -10, xmax=10,
	ymin= -10, ymax=10,
	xtick={-10,-9,...,10},
	ytick={-10,...,10},
	xlabel=\(x\),ylabel=\(y\)
	]
	\addplot[thick, domain= -10.5:10.5,samples=2] {1/3*x + 4/3};

	\end{axis}
	\end{tikzpicture}
	}
	\] 



% Problem 7
\prob Find a linear function, $f(x)$, such that $f(1)= 0$ and $f(-5)= 6$. \pspace



% Problem 8
\prob A single adult leader of a Math Circle is taking children to see a new math flick in theaters. Adult tickets are \$14 and children tickets are \$10. They get a deal for a \$6 mini box of popcorn and \$3 soda for each child. They will also pay \$20 to park the bus taken to bring the children there. Find an expression representing the total cost to bring $N$ children to this movie. Is this expression linear in $N$? Explain. \pspace 



% Problem 9
\prob Find the linear function that intersects $f(x)= 4 - x^2$ at $x= -1$ and $x= 3$. \pspace 



% Problem 10
\prob Is the point $(1, -4)$ on the graph of the linear function $\ell(x)= 3x + 1$? Explain. \pspace



% Problem 11
\prob The cost of taking $C$ credits at a college, in thousands of dollars, for $y$~years is given by $0.5 + 23y$.
	\begin{enumerate}[(a)]
	\item Find and interpret the slope and $y$-intercept. 
	\item What happens if the college increases the cost of tuition? Explain.
	\item What happens if the college decreases their base fees? Explain.  
	\end{enumerate} \pspace



% Problem 12
\prob While filling a large tank, an applied mathematician finds that the amount of water in a tank (in gallons) $t$~hours from now is given by $G(t)= 600t - 30$. 
	\begin{enumerate}[(i)]
	\item Find and interpret the slope and $y$-intercept.
	\item Find and interpret $G(4)$.
	\item Solve $G(t)= 30000$. What does this tell you?
	\end{enumerate}

\end{document}