\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,bmargin=1in,tmargin=1in]{geometry}
\usepackage{style}

\pagenumbering{gobble}


% -------------------
% Content
% -------------------
\begin{document}

% TItle
\begin{center} 
\bfseries
\color{scred}
\LARGE Syllabus Quick Facts \par\vspace{0.2\baselineskip}
\Large MATH 111I: Intensive Basic College Mathematics --- Spring 2025
\end{center} 


% Course Information
\mysection{0.27}{Course Information}{course_info}
\hspace{0.53cm} {\itshape Instructor Email}: \href{mailto:cm264@mailbox.sc.edu}{cm264@mailbox.sc.edu} \par
\hspace{0.53cm} {\itshape Course Webpage}: \href{https://coffeeintotheorems.com/courses/2024-2/fall/math-141/}{https://coffeeintotheorems.com/courses/2024-2/fall/math-141/} \par
\hspace{0.53cm} {\itshape Office Hours}: The instructor's office is LeConte 345C. The office hours are Monday, Wednesday, \par \hspace{0.55cm} and Friday from 12:00pm to 1:00pm, and Tuesday/Thursday from 11:30am until 12:30pm. \pspace


% Grading Components
\mysection{0.27}{Grading Components}{grade_comp}
Course grades are determined by the following components: \par \vspace{-0.3cm}
	\begin{table}[!ht]
        \begin{tabular}{lr}
	Check-Ins & 5\% \\
	Quizzes & 10\% \\
	Homework & 20\% \\
	Exam I--III & 40\% \\
	Final Exam & 25\%
        \end{tabular} 
        \end{table}


% Attendance 
\mysection{0.27}{Attendance}{attendance}
Attend each lecture and show up on time. Address any absences---anticipated or otherwise---with the instructor. If you miss a lecture, you are responsible for any material covered, any work assigned, any course changes made, etc. during the class. Five or more unexcused absences from lectures could result in receiving a grade penalty per additional absence or an `F' in the course. Furthermore, excessive lateness will also count as an absence. 
\pspace


% Check-Ins 
\mysection{0.27}{Check-Ins}{check}
There will be a check-ins \textit{every} class, typically at the start of class. Because solutions will often then be immediately discussed, no make-up check-ins will be given (except under extraordinary circumstances). \pspace


% Quizzes 
\mysection{0.27}{Quizzes}{quizzes}
There will be at least one quiz each week. These will typically be announced and on Thursdays. Students will have the opportunity to make-up a \textit{one pre-selected} quiz during the last full week of classes. More details on this opportunity will be given later in the semester.
\pspace


% Homeworks 
\mysection{0.27}{Homeworks}{homeworks}
These homeworks will likely be submitted virtually using WileyPlus. Assignments should be started as soon as possible; it is easier to keep up than it is to catch up. You are encouraged to work with others on homeworks. \pspace


% Exams 
\mysection{0.27}{Exams}{exams}
There will be three exams in this course, each worth $13.\overline{3}\,$\% of the course grade for a total of 40\% of the course grade. There will also be a final exam worth 25\% of the course grade. Together, all exams are worth 65\% of the course grade. 
\pspace


% Course Schedule 
\mysection{0.27}{Course Schedule}{schedule}
The following is a \emph{tentative} schedule for the course and is subject to change. 
        \begin{table}[!ht]
        \centering
        \scalebox{1}{%
        \begin{tabular}{ll || ll}
        Date & Topic(s) & Date & Topic(s) \\ \hline         
	01/13 & Course Introduction & 03/06 & Functions: C.1, 5.1--5.4 \\ 
	01/14 & Functions: 1.1--1.3 & 03/10 & Spring Break \\
	01/15 & Functions: 1.1--1.3 & 03/11 & Spring Break \\
	01/16 & Functions: 1.1--1.3 & 03/12 & Spring Break \\
	01/20 & Functions: 1.3--1.5 & 03/13 & Spring Break \\
	01/21 & Functions: 1.3--1.5 & 03/17 & Functions: 5.1--5.4 \\
	01/22 & Functions: 1.3--1.5 & 03/18 & Functions: 5.1--5.4 \\
	01/23 & Functions: 1.3--1.5 & 03/19 & Functions: 5.1--5.4 \\
	01/27 & Linear Functions: 2.1--2.3 & 03/20 & Functions: 5.1--5.4 \\
	01/28 & Linear Functions: 2.1--2.3 & 03/24 & Functions: 5.1--5.4 \\
	01/29 & Linear Functions: 2.1--2.3 & 03/25 & Review \\
	01/39 & Linear Functions: 2.1--2.3 & 03/26 & Review \\
	02/03 & Linear Functions: 2.3--2.5 & 03/27 & Exam 2 \\
	02/04 & Linear Functions: 2.3--2.5 & 03/31 & Exponential Functions: 6.1--6.3 \\
	02/05 & Linear Functions: 2.3--2.5 & 04/01 & Exponential Functions: 6.1--6.3 \\
	02/06 & Linear Functions: 2.3--2.6 & 04/02 & Exponential Functions: 6.1--6.3 \\
	02/10 & Linear Functions: 2.3--2.6 & 04/03 & Exponential Functions: 6.1--6.3 \\
	02/11 & Review & 04/07 & Exp./Logarithmic Functions: 6.4--7.1 \\
	02/12 & Review & 04/08 & Logarithmic Functions: 7.1--7.2 \\
	02/13 & Exam 1 & 04/09 & Logarithmic Functions: 7.1--7.2 \\
	02/17 & Quadratic Functions: 3.1--3.3 & 04/10 & Logarithmic Functions: 7.1--7.2 \\
	02/18 & Quadratic Functions: 3.1--3.3 & 04/14 & Logarithmic Functions: 7.1--7.2 \\
	02/19 & Quadratic Functions: 3.1--3.3 & 04/15 & Review \\
	02/20 & Quadratic Functions: 3.1--3.3 & 04/16 & Review \\
	02/24 & Quadratic Functions: 3.3--3.5 & 04/17 & Exam 3 \\
	02/25 & Quadratic Functions: 3.3--3.5 & 04/21 & Logarithmic Functions: 7.3--7.4 \\
	02/26 & Quadratic Functions: 3.3--3.5 & 04/22 & Logarithmic Functions: 7.3--7.4 \\
	02/27 & Quadratic Functions: 3.3--3.5 & 04/23 & Logarithmic Functions: 7.3--7.4 \\
	03/03 & Functions: C.1, 5.1--5.4 & 04/24 & Logarithmic Functions: 7.3--7.4 \\
	03/04 & Functions: C.1, 5.1--5.4 & 04/28 & Review \\
	03/05 & Functions: C.1, 5.1--5.4 & 05/01 & Final Exam
        \end{tabular}
        }
        \end{table}

\end{document}