\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,bmargin=1in,tmargin=1in]{geometry}
\usepackage{style}

\setlength{\parindent}{0ex}

% -------------------
% Content
% -------------------
\begin{document}

% Title
\begin{center} {\bfseries \LARGE MATH 141 --- Comment Card Responses --- Fall 2025} \end{center}

Here are select responses to comment cards given at the end of class. When computed, the class rating (out of 10) is given. The comment (often paraphrased for clarity) is given in italics/bold with the response following the comment. The responses are labeled by class date---with the class topic given. The classes are given in reverse-chronological order for ease of access to the most recent class. You may also click any of the hyperlinks below to jump to that date.

\begin{itemize}
\item \hyperref[09-08]{09/08, Monday: Derivative Rules}
\item \hyperref[09-05]{09/05, Friday: Derivative Definition}
\item \hyperref[09-03]{09/03, Wednesday: Continuity}
\item \hyperref[08-29]{08/29, Friday: Limit Techniques}
\item \hyperref[08-27]{08/27, Wednesday: Limit Techniques}
\item \hyperref[08-25]{08/25, Monday: Limit Techniques}
\item \hyperref[08-22]{08/22, Friday: Limit Techniques}
\item \hyperref[08-20]{08/20, Wednesday: Graphical Limits}
\end{itemize}

% 09/08, Monday: Continuity
\newpage
\section*{09/08, Monday: Derivative Rules\label{09-08}}

\begin{itemize}
\item {\bfseries\itshape Class Rating:} 9.14/10
\item {\bfseries\itshape Is email the best method of contact?}
\item {\bfseries\itshape Could you help us understand the definition and functions of derivatives more?}
\item {\bfseries\itshape What are other examples of continuous functions that are not differentiable?} 
\item {\bfseries\itshape Will the exam study guide be posted to Blackboard?}
\item {\bfseries\itshape I am struggling with limits on the homework, especially evaluating what the limit is from left or right side. Which video/lectures do you recommend going over?}
\item {\bfseries\itshape Life saver with the box method. Thank you!}
\item {\bfseries\itshape I don't like the chain rule}
\item {\bfseries\itshape It was a little fast paced}
\item {\bfseries\itshape I liked your chain rule method}
\item {\bfseries\itshape I liked the box method.}
\item {\bfseries\itshape Box method was great!}
\item {\bfseries\itshape Thank you for being a good calc teacher :P }
\item {\bfseries\itshape The Shrek Rule was helpful}
\item {\bfseries\itshape F**k da chain rule}
\item {\bfseries\itshape Thank you for being the best teacher I've had}
\item {\bfseries\itshape 1. Wall-E 2. The Incredibles 3. Inside Out} 
\item {\bfseries\itshape How do you get your coffee?} 
\item {\bfseries\itshape What is your favorite cheesecake?}
\item {\bfseries\itshape Do you like Steven Universe?}
\item {\bfseries\itshape Futurama ending has nothing over Attack on Titan}
\item {\bfseries\itshape $\uparrow\uparrow\downarrow\downarrow\leftarrow\rightarrow\leftarrow\rightarrow$ABstart}
\item {\bfseries\itshape You like rolling a lot. I agree.}

\end{itemize}

% 09/05, Friday: Continuity
\newpage
\section*{09/05, Friday: Derivative Definition\label{09-05}}

\begin{itemize}
\item {\bfseries\itshape Class Rating:} 9.07
\item {\bfseries\itshape Can we use the power rule?}
\item {\bfseries\itshape Is $\tfrac{f(x + h) - f(x)}{h}$ always used? Do we memorize this?}
\item {\bfseries\itshape Can you explain the other approaches of the derivatives?} 

\item {\bfseries\itshape I liked this better than the already printed packets}
\item {\bfseries\itshape I am retaking this course \& you explain this better than my previous teachers so thank you :) }
\item {\bfseries\itshape My last calculus professor made me drop out because of how horribly he `taught' us derivatives} 
\item {\bfseries\itshape You spoke slower!}
\item {\bfseries\itshape It was helpful to see the derivative background. I'd forgotten}
\item {\bfseries\itshape I have never had derivatives explained like this before. It was super helpful!}
\item {\bfseries\itshape More practice on derivatives please}
\item {\bfseries\itshape Why can't we just skip to the shortcut part?}
\item {\bfseries\itshape You were helpful babe}
\item {\bfseries\itshape Nothing was unhelpful sweet cheeks}
\item {\bfseries\itshape You are the goat}
\item {\bfseries\itshape Any fun plans this weekend?}
\item {\bfseries\itshape You're like batman but instead of fighting crime you teach math and ramble} 
\item {\bfseries\itshape Watch the movie Creep on Netflix}
\item {\bfseries\itshape The beginning was kind of confusing, but the end started to make sense.}
\item {\bfseries\itshape Your energy and charisma are most helpful} 
\item {\bfseries\itshape Have a great weekend goat}
\item {\bfseries\itshape I want cheesecake} 
\item {\bfseries\itshape Do you actually read these? Draw a smiley on Monday on the board if you do.}
\item {\bfseries\itshape I'm watching Jujutsu Kaisen---it's awesome} 
\item {\bfseries\itshape Do a Morgan Freeman impression}  %“Now, I know what you were expecting. A certain sound. A certain rhythm. That voice, warm as honey and steady as the earth itself. But let me tell you something… I’m not here to be Morgan Freeman. I’m here to tell you, in my own way, that no voice—no matter how beloved—can be borrowed and worn like a costume.
%
%You see, what makes him unique is not just his cadence, or his timbre, or even the way he can turn the simplest line into scripture. It’s that he is himself. And I? Well, I am me.
%
%So no… I won’t give you a Morgan Freeman impression. Instead, I’ll give you the truth: we don’t need to imitate greatness when we can speak in our own voices. And who knows? Maybe, just maybe, that’s how new legends are born.”

%“I know what you’re waitin’ for. That voice. The one folks say could make a grocery list sound like poetry. But that ain’t what you’ll find here. I won’t pretend to be him. All I can do is speak plain, in my own way… and maybe that’s enough.”

% Dont wait. Hope is a dangerous thing.
% I have no idea what those two italian ladies were singing about. Truth is, I don't want to know. Some things are best left unsaid.
% I find I'm so excited, I can barely sit still or hold a thought in my head. I think it's the excitement only a free man can feel, a free man at the start of a long journey whose conclusion is uncertain. I hope I can make it across the border. I hope to see my friend and shake his hand. I hope the Pacific is as blue as it has been in my dreams. I hope.
\item {\bfseries\itshape How tf are spheres 2-dimensional? Please elaborate} 
\item {\bfseries\itshape If there are infinitely many numbers between 0 and 1 and between 1 and 2, why isn't the amount of numbers between 0 and 2 bigger but isn't it also infinite?}

\end{itemize}

% 09/03, Wednesday: Continuity
\newpage
\section*{09/03, Wednesday: Continuity\label{09-03}}

\begin{itemize}
\item {\bfseries\itshape Class Rating:} 8.78/10
\item {\bfseries\itshape The Gateway video helped a great amount, thank you.}
\item {\bfseries\itshape Do we need to show work for every step?} 
\item {\bfseries\itshape When is the exam?}
\item {\bfseries\itshape Are the tests in-person and do we have longer than 50~minutes?} 
\item {\bfseries\itshape Will we cover squeeze theorem? We went over it in recitation} 
\item {\bfseries\itshape Does attendance in recitation affect grades?}
\item {\bfseries\itshape What is the format of the exam?} 
\item {\bfseries\itshape I need help preparing for the exam}
\item {\bfseries\itshape Maybe explain problems like `Find $a, b$ so that $f(x)$ is continuous'} 
\item {\bfseries\itshape Please draw more quick graphs that helps visualize a lot}
\item {\bfseries\itshape I liked the interaction in class}
\item {\bfseries\itshape Is the exam multiple choice or only given questions? Or a mixture?} 
\item {\bfseries\itshape Can we do more of these problems in class? More continuity?} 
\item {\bfseries\itshape Not excited for note taking} 
\item {\bfseries\itshape One of the easier lectures to understand}
\item {\bfseries\itshape I liked this}
\item {\bfseries\itshape Thanks for telling us what we need to know}
\item {\bfseries\itshape I found the examples extremely helpful.} 
\item {\bfseries\itshape Just the overall way you teach is super helpful} 
\item {\bfseries\itshape I hated the anime discussion. I hate anime and will never watch it.} 
\item {\bfseries\itshape Is Attack on Titan peak anime?}
\item {\bfseries\itshape ``Ah, dungeon food'' winged lion, Dungeon Meshi} 
\item {\bfseries\itshape You know Ball (Frieren)} 
\item {\bfseries\itshape AOT is the best show and anime ever made, if you disagree you're a child} 
\item {\bfseries\itshape Inuyasha > Frieren} 
\item {\bfseries\itshape Favorite Frieren character?} 
\end{itemize}

% 08/29, Friday: Limit Techniques
\newpage
\section*{08/29, Friday: Limit Techniques\label{08-29}}

\begin{itemize}
\item {\bfseries\itshape Class Rating:} 9.11/10
\item {\bfseries\itshape Where are the extra videos on Blackboard you said you would post that are really slow videos explaining everything?} 
\item {\bfseries\itshape Thank you for not making people feel dumb when they ask questions}
\item {\bfseries\itshape Why did we do a lab for the first lab class and then yesterday's class was all limit review?}

\item {\bfseries\itshape Where can we find extra practice problems for learned concepts?}
\item {\bfseries\itshape When is the first quiz?}
\item {\bfseries\itshape Have you ever used Bobo Botn Eastsdc"}
\item {\bfseries\itshape This was explained well!}
\item {\bfseries\itshape I suck at this}
\item {\bfseries\itshape Today was an ah-ha day}
\item {\bfseries\itshape How can I apply Calculus to Physics or simulation context?} 
\item {\bfseries\itshape Thanks for a great first full week of classes. This has actually been my favorite class so far. Have a great weekend.} 
\item {\bfseries\itshape Do we get a study guide for the exam?}
\item {\bfseries\itshape Are there any dropped check-ins?}
\item {\bfseries\itshape Will we have a review day before the exam?}
\item {\bfseries\itshape Do your research on LeBron Bymon James, aka King James}
\item {\bfseries\itshape Na, great lecture!}
\item {\bfseries\itshape Everything today clicked for me so very good} 
\item {\bfseries\itshape This was very cool! Examples were the best!}
\item {\bfseries\itshape Can we get a full lesson recap before our exams, in-person or online?}
\item {\bfseries\itshape Chipotle is not that good}
\item {\bfseries\itshape The best selling sandwich in England is the the BLT which includes both a fruit and a vegetable}
\item {\bfseries\itshape You lack ball knowledge}
\item {\bfseries\itshape Jalen hurts or Justen bulbert} 
\item {\bfseries\itshape I get within 10~km on Geoguesser}
\item {\bfseries\itshape How many languages do you speak?}
\item {\bfseries\itshape Chipotle servings have gotten too small}
\item {\bfseries\itshape Chipotle is the best}
\item {\bfseries\itshape Dap me up} % Image
\item {\bfseries\itshape Skyline is the best fast food! I'm from Cincinnati} 

\end{itemize}

% 08/27, Wednesday: Limit Techniques
\newpage
\section*{08/27, Wednesday: Limit Techniques\label{08-27}}

\begin{itemize}
\item {\bfseries\itshape Class Rating:} 8.81
\item {\bfseries\itshape There are a lot of different ways to solve limits.}
\item {\bfseries\itshape I don't know when to use each type of limit}
\item {\bfseries\itshape I am guessing 6.5/10 doesn't count for the Gateway?}
\item {\bfseries\itshape When is the second Gateway?}
\item {\bfseries\itshape You Rick rolled me on Blackboard}
\item {\bfseries\itshape Math is hard}
\item {\bfseries\itshape It was all understandable today!}
\item {\bfseries\itshape I would appreciate more algebra explanation on cancelling numbers to `make it work' for $e$ limits}
\item {\bfseries\itshape Mask made it harder to hear}
\item {\bfseries\itshape Feel better soon!}
\item {\bfseries\itshape You da man}
\item {\bfseries\itshape What do you enjoy about [?]} 
\item {\bfseries\itshape Get well soon!}
\item {\bfseries\itshape Thank you for the Gateway video!}
\item {\bfseries\itshape Confused most of the time but it comes together in the end}
\item {\bfseries\itshape This wasn't as confusing and as complicated as the last class}
\item {\bfseries\itshape Do you watch anime or only live TV?}
\item {\bfseries\itshape I like your `dumb' analogies}
\item {\bfseries\itshape Python sucks}
\item {\bfseries\itshape Yooooooo}
\item {\bfseries\itshape You should try hockey, it's like polo with more fights and more missing teeth}
\item {\bfseries\itshape Get well soon!}
\item {\bfseries\itshape You remind me of a hyperactive Yorkie} % certain set of skills
\end{itemize}

% 08/25, Monday: Limit Techniques
\newpage
\section*{08/25, Monday: Limit Techniques\label{08-25}}

\begin{itemize}
\item {\bfseries\itshape Class Rating:} 8.63
\item {\bfseries\itshape Do we need a calculator for this class?}
\item {\bfseries\itshape How do I know which homework correlates with each class period/lesson?} 
\item {\bfseries\itshape Could you go over all the steps? Sometimes you skip steps}
\item {\bfseries\itshape Where can I practice limit problems?}
\item {\bfseries\itshape How do you remember and especially identify when we see certain problems?}
\item {\bfseries\itshape If there were a campus shooting, where would we hide?}
\item {\bfseries\itshape You're my knight in shining armor} 
\item {\bfseries\itshape Are all the notes for the semester posted to Blackboard?}
\item {\bfseries\itshape Will points be taken off if we don't show the exact steps you show?}
\item {\bfseries\itshape Should we know the unit circle?}
\item {\bfseries\itshape How did you go from $\tfrac{\frac{1}{h + 5} - \frac{1}{5}}{h}$ to $\tfrac{\tfrac{5 - (h + 5)}{5(h + 5)}}{h}$?}
\item {\bfseries\itshape Well explained!}
\item {\bfseries\itshape Confused about the last limit with $e$} 
\item {\bfseries\itshape The examples are so helpful} 
\item {\bfseries\itshape Liked the werk method}
\item {\bfseries\itshape I would prefer to write my own notes}
\item {\bfseries\itshape Very helpful!}
\item {\bfseries\itshape I'm looking forward to the semester}
\item {\bfseries\itshape I liked the lecture a lot I learned this concept in AP Calc and it was good way of teaching it. Also good emphasis on mental health}
\item {\bfseries\itshape People have been talking about homework being due but I don't see any due until September} 
\item {\bfseries\itshape Just gotta practice} 
\item {\bfseries\itshape Please write a control of the problem and another that you work off of}
\item {\bfseries\itshape You contradicted some past statements}
\item {\bfseries\itshape You over-explained}
\item {\bfseries\itshape Way better than my HS teacher!}
\item {\bfseries\itshape Special limits was so friggin' tuff}
\item {\bfseries\itshape I liked how you do an example and then we do a practice problem}
\item {\bfseries\itshape You good baby girl}
\item {\bfseries\itshape You Rick rolled me :| }
\item {\bfseries\itshape Still need help with conjugation!}
\item {\bfseries\itshape What are different ways to memorize these?}
\item {\bfseries\itshape Caleb, you talk very fast}
\item {\bfseries\itshape Favorite professional sports team?}
\item {\bfseries\itshape 67!}
\item {\bfseries\itshape Mandiballs}
\item {\bfseries\itshape $0 \cdot \infty= 1$???}
\item {\bfseries\itshape You gotta watch a trailer for Weapons}
\item {\bfseries\itshape Recommended movies?}
\item {\bfseries\itshape It's crazy how you kept track of every movie and TV show that you've ever watched, presumably since childhood}
\item {\bfseries\itshape Least favorite food?}
\item {\bfseries\itshape You scare me}
\item {\bfseries\itshape I still think you look like Ian Hecox} 
\item {\bfseries\itshape Thank god for Project Runway} 
\item {\bfseries\itshape Are you into DND?}
\item {\bfseries\itshape Why was 6 afraid of 7?}
\item {\bfseries\itshape What's your favorite word in German?}
\end{itemize}

% 08/22, Friday: Limit Techniques
\newpage
\section*{08/22, Friday: Limit Techniques\label{08-22}}

\begin{itemize}
\item {\bfseries\itshape Class Rating:} 8.92/10
\item {\bfseries\itshape What's the point of the Python labs?}
\item {\bfseries\itshape How do you plug in $\infty$ into a limit?}
\item {\bfseries\itshape Will I need to know things like $\arctan$ for exams because I passed the gateway without it but I have never been taught it.}
\item {\bfseries\itshape What is the best tool to use to brush up on my trig. values, inverse, etc. precalc stuff?}
\item {\bfseries\itshape What is the difference between DNE and undefined?} 
\item {\bfseries\itshape What do you mean by you dropped your limits?} 

\item {\bfseries\itshape I liked that we had a chance to work out problems ourselves}
\item {\bfseries\itshape The examples were very helpful.}
\item {\bfseries\itshape If you could do like a refresher on some of the way to get the equation before getting the answer} 
\item {\bfseries\itshape Being okay with being wrong makes me actually interested}
\item {\bfseries\itshape Great pacing today} 
\item {\bfseries\itshape Some parts went kinda fast}
\item {\bfseries\itshape I feel like we went kind of quick over the asymptotes} 
\item {\bfseries\itshape Didn't know that $\sqrt{}$ can be in the denominator.}
\item {\bfseries\itshape It was nice to do some problems in class.}
\item {\bfseries\itshape I would like to write my own notes.} 
\item {\bfseries\itshape I think you answered questions really well and made it easy to understand} 
\item {\bfseries\itshape I both do and don't understand what I'm learning (not your fault though)} 
\item {\bfseries\itshape I am nervous, my last calc class was AB in junior year} 
\item {\bfseries\itshape Great job answering questions} 
\item {\bfseries\itshape The lab was confusing} 
\item {\bfseries\itshape Thanks for addressing common mistakes} 
\item {\bfseries\itshape Your vibe is not very boring so it makes it better to understand}
\item {\bfseries\itshape You talk really fast but if I lock in I'm good.} 
\item {\bfseries\itshape On the answer key on Blackboard, the example $\ds\lim_{b \to 0} \tfrac{(3 + b)^2 - 9}{b}= 9$ is wrong, it says 2 not 6.} 

\item {\bfseries\itshape Do you speak German? I heard you listening to an eBook when in your office} 
\item {\bfseries\itshape Day 1 of asking you to come to class barefoot}
\item {\bfseries\itshape Caleb is a sigma goated beast} 
\item {\bfseries\itshape Dr. McWhorter's celebrity lookalike is James C[G?]ordon} 
\end{itemize}

% 08/20, Wednesday: Graphical Limits
\newpage
\section*{08/20, Wednesday: Graphical Limits\label{08-20}}

\begin{itemize}
\item {\bfseries\itshape Class Rating:} 8.69/10
\item {\bfseries\itshape How do you know if a function is `DNE' if there is a left and right limit?}
\item {\bfseries\itshape Sometimes when you pointed at the screen, I couldn't see and while I could figure it out, it added to the confusion at times:}
\item {\bfseries\itshape How is it sometimes DNE and $\infty$:}
\item {\bfseries\itshape In the note directly under function behavior, does that say `examing'?:}

\item {\bfseries\itshape Do you want us to raise our hands, or just blurt out the answer?} 
\item {\bfseries\itshape Why do we write $x \to$ example and not use the variable $y$ as the answer?}
\item {\bfseries\itshape I think your communication is great, it is just hard to see the writing on board:} 
\item {\bfseries\itshape Personally, I learn better with step by step explanations, will these be common in this class or would I benefit further from SI or outside sources?}
\item {\bfseries\itshape Do you think you can go through one or two problem step by step before moving on to a new topic?} 
\item {\bfseries\itshape Could you break down how to write answers to limits?} 
\item {\bfseries\itshape I've never taken a calculus course, so I'm unsure of what material to brush up on before this class.} 
\item {\bfseries\itshape Funny prof, made it understandable:} 
\item {\bfseries\itshape It was a little fast. You jumped into limits without explaining where the limit is and what it is.}
\item {\bfseries\itshape I wish the class was longer}
\item {\bfseries\itshape I think I will enjoy this teaching style:}
\item {\bfseries\itshape Thank you for not requiring a textbook. Thanks for being cool.} 
\item {\bfseries\itshape I would have liked to write a little more:}
\item {\bfseries\itshape The large packets are somewhat daunting} 
\item {\bfseries\itshape The visual AIDS were most helpful}
\item {\bfseries\itshape Caleb silly}

\item {\bfseries\itshape I loved the way you made it entertaining.} [Areyounotentertained]
\item {\bfseries\itshape I really appreciate the resources you offered. I am a junior and have struggled with some stuff so I really appreciate it! Also you're super cool! :) }
\item {\bfseries\itshape You're very good at explaining stuff and the examples were great!}
\item {\bfseries\itshape Has anyone ever told you that you remind them of Ian Hecox from Smosh?} [handsomeSquidward]
\item {\bfseries\itshape You are 1,000x better than my Pre-Calc professor \& looking forward to a great semester!}
\item {\bfseries\itshape Is $1= 0.\overline{9}$}
\end{itemize}

















\end{document}