\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,bmargin=1in,tmargin=1in]{geometry}
\usepackage{style}

\pagenumbering{gobble}

% -------------------
% Content
% -------------------
\begin{document}

% TItle
\begin{center} 
\bfseries
\color{scred}
\LARGE Syllabus Quick Facts \par\vspace{0.2\baselineskip}
\Large MATH 344: Applied Linear Algebra --- Spring 2026
\end{center} \pspace


% Course Information
\mysection{0.27}{Course Information}{course_info}
\hspace{0.53cm} {\itshape Instructor Email}: \href{mailto:cm264@mailbox.sc.edu}{cm264@mailbox.sc.edu} \par
\hspace{0.53cm} {\itshape Course Webpage}: \href{https://coffeeintotheorems.com}{https://coffeeintotheorems.com} \par
\hspace{0.53cm} {\itshape Office Hours}: The instructor's office is LeConte 345C. The office hours are Monday, Wednesday, \par \hspace{0.55cm} and Friday from 2:30pm to 3:30pm, and Tuesday/Thursday from 12:00pm until 1:00pm. \pspace


% Grading Components
\mysection{0.27}{Grading Components}{grade_comp}
Course grades are determined by the following components: \par \vspace{-0.3cm}
	\begin{table}[!ht]
        \begin{tabular}{lr}
	Check-Ins & 10\% \\
	Homework & 25\% \\
	Exam 1 & 20\% \\
	Exam 2 & 20\% \\
	Final Exam & 25\%
        \end{tabular} 
        \end{table}


% Attendance 
\mysection{0.27}{Attendance}{attendance}
Attend each lecture and show up on time. Address any absences---anticipated or otherwise---with the instructor. If you miss a lecture, you are responsible for any material covered, any work assigned, any course changes made, etc. during the class. Five or more unexcused absences from lectures could result in receiving a grade penalty per additional absence or an `F' in the course. Furthermore, excessive lateness will also count as an absence. 
\pspace

% Check-Ins 
\mysection{0.27}{Check-Ins}{check}
There will be a check-ins \textit{every} class, typically at the start of class. Because solutions will often then be immediately discussed, no make-up check-ins will be given (except under extraordinary circumstances). \pspace

% Homeworks 
\mysection{0.27}{Homeworks}{homeworks}
there will be weekly homework assignments. Homeworks will mostly be given and submitted using MyOpenMath. This assessment system is free for students and is integrated into Blackboard. Students will not need to create an account or make any purchases. 
\pspace


% Exams 
\mysection{0.27}{Exams}{exams}
There will be two exams in this course, each worth 20\% of the course grade, for a total of 40\% of the course grade. There will also be a final exam worth 25\% of the course grade. Together, all exams are worth 65\% of the course grade. 
\pspace



\newpage



% Course Schedule 
\mysection{0.27}{Course Schedule}{schedule}
The following is a \emph{tentative} schedule for the course and is subject to change. 
        \begin{table}[!ht]
        \centering
        \scalebox{1}{%
        \begin{tabular}{ll || ll}
        Date & Topic(s) & Date & Topic(s) \\ \hline    
        01/12 & Vectors & 03/06 & Column Space \\
        01/14 & Vectors & 03/09 & Spring Break \\
        01/16 & Vectors & 03/11 & Spring Break \\
        01/19 & MLK Day (No Classes) & 03/13 & Spring Break \\
        01/21 & Matrices & 03/16 & Dimension \\
        01/23 & RREF & 03/18 & Dimension \\
        01/26 & RREF & 03/20 & Fundamental Theorem \\
        01/28 & RREF & 03/23 & Fundamental Theorem \\
        01/30 & Inverses & 03/25 & Overflow \\
        02/02 & Inverses & 03/27 & Exam 2 \\
        02/04 & Determinants & 03/30 & Eigenvectors \\
        02/06 & Determinants & 04/01 & Eigenvectors \\
        02/09 & Determinants & 04/03 & Eigenvectors \\
        02/11 & Overflow & 04/06 & Eigenvectors \\
        02/13 & Exam 1 & 04/08 & Diagonalization \\
        02/16 & LU Factorizations & 04/10 & Diagonalization \\
        02/18 & LU Factorizations & 4/13 & Diagonalization \\
        02/20 & LU Factorizations & 04/15 & Orthogonality \\
        02/23 & $Ax= b$ \& Rank & 04/17 & Orthogonality \\
        02/25 & Subspaces & 04/20 & Orthogonality \\
        02/27 & Nullspace & 04/22 & Orthogonality \\
        03/02 & Nullspace & 04/24 & Special Topics \\
        03/04 & Column Space & 04/27 & Special Topics 
        \end{tabular}
        }
        \end{table}

\end{document}