\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,bmargin=1in,tmargin=1in]{geometry}
\usepackage{style}

\pagenumbering{gobble}


% -------------------
% Content
% -------------------
\begin{document}

% TItle
\begin{center} 
\bfseries
\color{stacred}
\LARGE Syllabus Quick Facts \par\vspace{0.2\baselineskip}
\Large MATH 141: Calculus I --- Spring 2024
\end{center} \pspace


% Course Information
\mysection{0.27}{Course Information}{course_info}
\hspace{0.53cm} {\itshape Instructor Email}: \href{mailto:cm264@mailbox.sc.edu}{cm264@mailbox.sc.edu} \par
\hspace{0.53cm} {\itshape Course Webpage}: \href{https://coffeeintotheorems.com/courses/2024-2/fall/math-141/}{https://coffeeintotheorems.com/courses/2024-2/fall/math-141/} \par
\hspace{0.53cm} {\itshape Office Hours}: 	\par \vspace{-0.3cm}
	\begin{table}[!ht]
	\centering
	\begin{tabular}{l || l}
	Mon. & 11:30~am -- 12:30~pm \\
	Tues. & 11:30~am -- 12:30~pm \\
	Wed. & 11:30~am -- 12:30~pm \\
	Thurs. & 11:30~am -- 12:30~pm
	\end{tabular}
	\end{table}


% Grading Components
\mysection{0.27}{Grading Components}{grade_comp}
Course grades are determined by the following components: \par \vspace{-0.3cm}
	\begin{table}[!ht]
        \begin{tabular}{lr}
	CircleIn & 5\% \\
	Quizzes & 5\% \\
	Labs & 10\% \\
	Gateway I \& II & 10\% \\
	Homework & 15\% \\
	Exam I--III & 30\% \\
	Final Exam & 25\%
        \end{tabular} 
        \end{table}


% Attendance 
\mysection{0.27}{Attendance}{attendance}
Attend each lecture and show up on time. Address any absences---anticipated or otherwise---with the instructor. If you miss a lecture, you are responsible for any material covered, any work assigned, any course changes made, etc. during the class. Seven or more unexcused absences from lectures could result in receiving a grade penalty per additional absence or an `F' in the course. Furthermore, excessive lateness will also count as an absence. 
\pspace


% CircleIn 
\mysection{0.27}{CircleIn}{circlein}
Students are expected to participate in the course using CircleIn. This participation consists of two components: weekly feedback and CircleIn Study Actions. Students need to submit weekly check-ins and complete a total of at least 10 CircleIn Study Actions throughout the semester. 
\pspace



% Quizzes 
\mysection{0.27}{Quizzes}{quizzes}
There will be a quiz \textit{every} class, typically at the start of class. Because solutions will often then be immediately discussed, no make-up quizzes will be given (except under extraordinary circumstances). \pspace



% Labs 
\mysection{0.27}{Labs}{labs}
Nearly every week, students will have a lab to complete using SageMath. These labs will help engage them with the material and learn some basic programming skills. Students will have a designated lab time to work on these labs. However, if a student does not complete their lab during this time, they are still expected to complete and submit the lab on time.
\pspace



% Gateways 
\mysection{0.27}{Gateways}{gateways}
There are two Gateway exams during the semester. The Gateway exams are 30~minute exams that will help students to achieve mastery over basic Precalculus (Gateway~I) and differentiation (Gateway~II) skills and help assure students that they are prepared for the future material. {\itshape Students must complete and meet the minimum requirement for the Gateway exams to pass the course.}
\pspace


% Homeworks 
\mysection{0.27}{Homeworks}{homeworks}
there will be weekly homework assignments. Homeworks will mostly be given and submitted using MyMathLab. Therefore, students will need to purchase an access code to this system at \url{http://www.mymathlab.com}. Students can also purchase access to a digital copy of the textbook when they purchase an access code.
\pspace


% Exams 
\mysection{0.27}{Exams}{exams}
There will be three exams in this course, each worth 15\% of the course grade, for a total of 45\% of the course grade. There will also be a final exam worth 20\% of the course grade. Together, all exams are worth 65\% of the course grade. The final exam grade will be used to replace the lowest of the three exam scores---assuming the final exam score is greater than this lowest score.
\pspace


% Course Schedule 
\mysection{0.27}{Course Schedule}{schedule}
The following is a \emph{tentative} schedule for the course and is subject to change. 
        \begin{table}[!ht]
        \centering
        \scalebox{0.743}{%
        \begin{tabular}{ll || ll}
        Date & Topic(s) & Date & Topic(s) \\ \hline         
	08/20 & Course Introduction & 10/15 & Recitation \\
	08/21 & Limit Introduction (\S2.1--2.4) & 10/16 & IVT, MVT (\S2.5, 4.2) \\
	08/22 & Gateway I & 10/17 & Fall Break (No Class) \\	
	08/26 & Limit Rules (\S2.2) & 10/21 & Exam Review \\
	08/27 & Recitation & 10/22 & Exam Review \\
	08/28 & Gateway I & 10/23 & Exam 2 \\
	08/29 & Special Limits (\S2.2, 2.6) & 10/24 & Lab 5 \\
	09/02 & Labor Day (No Class) & 10/28 & Integral Introduction (\S5.1--5.3) \\
	09/03 & Recitation & 10/29 & Recitation \\
	09/04 & Review \& Continuity (Ch. 2, \S2.5) & 10/30 & Integral Introduction (\S5.1--5.3) \\
	09/05 & Lab 1 & 10/31 & Lab 6 \\
	09/09 & Derivative Introduction (\S3.1--3.2, 3.4) & 11/04 & Fund. Thm. of Calc. (\S5.4) \\
	09/10 & Recitation & 11/05 & Election Day (No Class) \\
	09/11 & Derivative Rules (\S3.3, 3.5, 3.8, 3.9) & 11/06 & Area between Curves (\S5.6) \\
	09/12 & Lab 2 & 11/07 & Lab 7 \\	
	09/16 & Derivative Rules (\S3.3, 3.5, 3.8, 3.9) & 11/11 & $u$-substitution (\S5.5--5.6) \\
	09/17 & Recitation & 11/12 & Recitation \\
	09/18 & Interpreting Derivatives (\S4.1, 4.3, 4.4) & 11/13 & $u$-substitution (\S5.5--5.6) \\
	09/19 & Lab 3 & 11/14 & Lab 8 \\
	09/23 & Linearization/Differentials (\S3.11) & 11/18 & Exam Review \\
	09/24 & Exam Review & 11/19 & Exam Review \\
	09/25 & Exam 1 & 11/20 & Exam 3 \\
	09/26 & Lab 4 & 11/21 & Lab 9 \\
	09/30 & Implicit Differentiation (\S3.7) & 11/25 & Thanksgiving Break (No Class) \\
	10/01 & Recitation & 11/26 & Thanksgiving Break (No Class) \\
	10/02 & Related Rates (\S3.10) & 11/27 & Thanksgiving Break (No Class) \\
	10/03 & Gateway II & 11/28 & Thanksgiving Break (No Class) \\
	10/07 & Optimization (\S4.6) & 12/02 & Volumes using Integration (\S6.1--6.2) \\
	10/08 & Recitation & 12/03 & Recitation \\	
	10/09 & Optimization (\S4.6) & 12/04 & Volumes using Integration (\S6.1--6.2) \\
	10/10 & Gateway II & 12/05 & Lab 10 \\
	10/14 & l'H\^{o}pital (\S4.5) & 12/9 or 12/13 & Final Exam
        \end{tabular}
        }
        \end{table}


\end{document}